\section{Design files}

% The  complete  design  files  must  be  either  uploaded  to  an  approved  online  repository,  uploaded  at the  time  of  submission  on  the  online  Editorial  Manager  submission  interface  as  supplementary materials [CAD files, videos,. . . ], or included in the body of the manuscript [e.g.  figures].  The three approved  online  repositories  are  Mendeley  Data,  the  Open  Science  Framework,  and  Zenodo. See repository instructions: https://doi.org/10.5281/zenodo.3346799

% Design files should be in preferred format for making modifications. See OSHWA’s open-source definition for details: https://www.oshwa.org/definition/

for dome design we use, design from paul bourke http://paulbourke.net/dome/iDome/
\textit{The complete design files must be either uploaded to an approved online repository, uploaded at the time of submission on the online \href{https://editorialmanager.com/ohx/}{Editorial Manager} submission interface as supplementary materials [CAD files, videos,\dots], or included in the body of the manuscript [e.g. figures]. The three approved online repositories are \href{https://data.mendeley.com/}{Mendeley Data}, the \href{http://osf.io}{Open Science Framework}, and \href{https://zenodo.org/}{Zenodo}. See repository instructions \href{https://doi.org/10.5281/zenodo.3346799}{here}. Design files should be in preferred format for making modifications. See \href{https://www.oshwa.org/definition/}{OSHWA’s open-source definition} for details.}
\begin{itemize}
\item \textit{CAD files. Authors are encouraged to use free and open source software packages for creating the files. For CAD files, OpenSCAD, FreeCAD, or Blender are encouraged, but if not available source files from proprietary CAD packages such as Autocad or Solidworks and other drawing packages are acceptable.
\item 3D printing. Supplementary files that facilitate the digital replication of the devices are encouraged. For example, STL files for 3-D printing components. We recommend uploading CAD files to the NIH 3D Print Exchange as Custom Labware and providing a link to the location.
\item Electronics. PCB layouts and other electronics design files can be uploaded to the Open Hardware Repository or other repositories.
\item Software and firmware. All software files used in the design and operation of the hardware should be included in the repository. Provide a description of software and firmware and use extensive comments in the code.}
\end{itemize}

%\begin{landscape}
\subsection{Design Files Summary}
% Please include a summary of all design files for your hardware by filling rows of the table below

\tabulinesep=1ex
\begin{tabu} to \linewidth {|X|X|X[1.5,1]|X[1.5,1]|} 
\hline
\textbf{Design file name} & \textbf{File type} & \textbf{Open source license} & \textbf{Location of the file} \\\hline
%Insert design files
\textit{Design file 1} & \textit{e.g. CAD file, figures, videos} & \textit{All designs must be submitted under an open hardware license. Enter the corresponding open source license for the file.} & \textit{Enter a link to the online location or the sentence: ``available with the article'', as appropriate}  \\\hline
\textit{Design file 2} & \dots & \dots & \dots \\\hline
% Design file 3 & File type & License & Link \\\hline
\end{tabu}

% For each design file listed in the summary above, include a short description of the file below (one or two sentences)
\textit{For each design file listed above, include a short description of the file here (one or two sentences)}
%\end{landscape}